Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-29 manuscript.Rmd
Change filenames and add small revision

# read in social cohesion data
raw_cohesion_data <- read.csv("./data/raw/syria_cohesion.csv")

@@

# calculate mean cohesion
raw_cohesion_ts <- raw_cohesion_data %>%
  group_by(date) %>%
  summarise(
    MeanCohesion = mean(Cohesion_avg),
    sd = sd(Cohesion_avg),
    var = sd^2,
    n = n(),
    se = sd / n) %>%
  ggplot(aes(x = date, y = MeanCohesion)) +
  geom_errorbar(aes(ymin = MeanCohesion-var, ymax = MeanCohesion+var), color = "grey57") +
  geom_point() +
  geom_line() +
  xlab("Date") +
  ylab("Mean Social Cohesion")

@@

#### Parameters
To conduct the analyses on the decile data, the parameters were set to those
typically used in categorical CRQA: Delay was set to $0$, embedding dimension
was set to $1$, and radius was set to $.001$ to allow for only exact recurrent
matches. No normalization was done, and lines were considered two or more
consecutive recurrent points. The Theiler window was set to $0$ to include
points along the line of identity. For more details on the CRQA parameters and
how they impact analyses, see @R-crqa.

@@

The second parameter to be chosen is a *window step size*. Window step size is
how far the window moves up the line of identity before conducting CRQA again.
We chose $1$ for the step size to understand how the metrics evolve from day to
day.

>>>>

# read in social cohesion data
raw_cohesion_data <- read.csv("./data/raw/syria_coherence_sort_5.csv")

@@

# calculate mean cohesion
raw_cohesion_ts <- raw_cohesion_data %>%
  group_by(date) %>%
  summarise(
    MeanCohesion = mean(Cohesion..avg.),
    sd = sd(Cohesion..avg.),
    var = sd^2,
    n = n(),
    se = sd / n) %>%
  ggplot(aes(x = date, y = MeanCohesion)) +
  geom_errorbar(aes(ymin = MeanCohesion-var, ymax = MeanCohesion+var), color = "grey57") +
  geom_point() +
  geom_line() +
  xlab("Date") +
  ylab("Mean Social Cohesion")

@@

#### Parameters
To conduct the analyses on the decile data, the parameters were set to those
typically used in categorical CRQA: Delay was set to $0$, embedding dimension
was set to $1$, and radius was set to $.001$ to allow for only exact recurrent
matches. No normalization was done, and lines were considered two or more
consecutive recurrent points. The Theiler window was set to $0$ to include
points along the line of synchrony. For more details on the CRQA parameters and
how they impact analyses, see @R-crqa.

@@

The second parameter to be chosen is a *window step size*. Window step size is
how far the window moves up the line of synchrony before conducting CRQA again.
We chose $1$ for the step size to understand how the metrics evolve from day to
day.
